%& --translate-file il2-t1
\documentclass[a4paper,10pt]{article}
%\usepackage[polish]{babel}
%\usepackage{polski}
\usepackage{makeidx}
%\usepackage[utf-8]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage[a4paper,left=2.5cm,right=2.0cm,top=1.5cm,bottom=1.5cm]{geometry}
% Title Page
\title{Project SkyNet design notes}
\author{Jacek Czaja}
\makeindex

\begin{document}

\maketitle

\tableofcontents

\section{Introduction}
SkyNet is to be testing platform for various algorithms. Including:
\begin{itemize}
\item Machine Learning (Neural Networks, Support Vector Machines, Perceptions)
\item Artificial Intelligence (A* , Alpha-Beta )
\item Quantum Computation (simulation of algorithms of Quantum computer)
\end{itemize}

Testing is meant to be functional (If generated data match reference data) and performance (time which takes for OpenCL based solution to do its computation)

\section{Architecture Design}
Architecture will have modular design.
Main module will deliver interface for plugins.
Plugins(Modules) will implement interface.
Plugins will be independent to each other.
Interface will be something like:
\begin{verbatim}
class ModuleInterface
{
    RunTest()
    PrintDescription()
};
\end{verbatim}

Main Module at the beginning will load all modules from directory where modules are kept.
How Main Module is to determine what's inside of given module is  yet to be described.

SkyNet holds lists of diffrent types of modules eg. classifiers (PLA, SVM)

Tests for diffrent devices to be run on separate threads

Test modules will conduct/implement testing scenarios like. randomClassification etc. Module will return training samples,
performa validation, verification 

So, module will be given data and commandqueue to send kernel to, context and device that compilation is taking place against

There will be a module handling OpenCL :
Implementing SkyNetOpenCLHelper module , which is opencl interacting routines to creat context, buildp rograms, kernels etc. and handling errors


Charts module. Module to generate , dump data. Can also draw gnuplot script.
Scheme of working:
\begin{enumerate}
\item Each module may have its instance
\item Constructor to create directory: module about string + PID
\item We put history of flags and for each weights that will be dumped and charts can be generated for them
\item Generation of movie by script is also to be done
\end{enumerate}

compilation flags for building program are taken from device version passed to OpenCL Helper module




\begin{itemize}
\item creation of command queue
\item program building/creating
\item kernel creation
\item handling or errors
\end{itemize}

There are modules delivering tests to be done and validating results.
For example randomPointsClassification module. Its purpose is to:
\begin{itemize}
\item generated random input
\item initalize weights
\item validate generated weights eg. check if weights do well on testing example
\item test generalization of selected hypothesis 
\item Training Points can also be stored
\item test module also to have Diagnostic class instance so to have picture of generalization
\end{itemize}

Where to deliver reference CPU implementation? I think good place for CPU reference implementation is module itself.
So Protocol will be extended with method RunReferencePLA

Classification modules when requested will return reference to classification data of last processed set. Eg.

consider unique pointer instead normal one
Implement charts generation (Error how does it change) 

- Implement user interface 
\section{Usage Interface}
SkyNet can be operated from command line. Options:
\begin{itemize}
\item list\_modules (lists available modules)
\item help (print info about usage of SkyNet)
\item module <number of module to be loaded> (run tests against indicated module. Numbers to be taken from list\_module option)
\item loading weights from file
\end{itemize}

\section{Serialization}
It is all about storing learned weights so they can be loadedl ateron and learning can be resumed.
Loosy. So RunRef RunCL methods will be updated with callback routine to be calledi n between interations
Some verification if data suits for selected algorithm should be added. 
There is a protocol class for checking if specific key was pressed and returns true if that is the case
At the same time weights storring takes place . If no key was pressed then weights that were learned are also stored at very end.
From Commandline interface it is possible to resume learning starting from loaded (previously stored weights).
So in file with weights we have a name of algorithm (first line starting with \#) and weights itself (second line). So
based on this info we can resume training of specific algorithm using given weights from file as starting weights.

\section{Stopping Ciriteria}
Implement Early stop method\\
Things to do:
\begin{enumerate}
\item Create validation set next to test and training sets
\item Implement calcullating of validation error and dumping it into file with training error 
\item Draw a chart of training error and validation error to see when overfitting starts 
\end{enumerate}

Next Step: Compile, test , verify validation and training error progress 
Next Step: Verify generated of General loss earl stop
Next Step: Describe here used algorithm




\section{Installation}
\subsection{Building with GCC for generation of clang\_complete\_config}
\begin{verbatim}
CXX='/home/jczaja/.vim/bundle/clang_complete/bin/cc_args.py g++'   cmake ../code/
make VERBOSE=1
make copy_clang_complete
\end{verbatim}
\subsection{Building with Clang}
\begin{verbatim}
CXX='/home/jczaja/.vim/bundle/clang_complete/bin/cc_args.py clang++'   cmake ../code/
make VERBOSE=1
make copy_clang_complete
\end{verbatim}


\section{TODO}
\begin{itemize}
\item make proper stopping criteria
\item Make exceptions,errors handling for SKyNetOpenCLHelper module
\item Compilation flags for kernels should come from SkyNet module alond with device send or generate flags itself in helper
\item make common module handling init of opencl and kernel/program building
\item Make a git branches: master and milestone(release)
\item make/lear proper c++ exceptions usage to handle errors of OpenCL initialization
\item each module should provide also CPU plain implementation of algorithm
\item Modules are algorithms and Devices( hardware layer) are to be initialized in SkyNet core
\item Add routines for measuring time eg. time of day etc
\item Create Contexts assigned to given devices/platforms
\item Mapping of errors(ints) to strings
\item As for drawing animation out generated weights. We could make a global output buffer
containing weights as they are being updated
\item Create a module creating gnuplot charts/ generting scripts making a movie out of generated charts
\item make gnuplot script generation of charts of learning steps , and make video out of it
\item coding standard fixes:
\begin{enumerate}
\item empty functions , braces in the same line
\item force space removal in args of function call
\item brace after for loop is not moved to new line
\end{enumerate}
\end{itemize}

\end{document}

